### 2024-02-12 docs/exec-summary/seasonality.qmd
Explain the seasonality detection procedure, close #13, CU-86cujzpdx[closed]

Exploration on seasonality is done on monthly data with a first-order difference.

>>>>

Exploration on seasonality was done on detrended daily, weekly, and monthly data by generating seasonal plots and calculating the autocorrelation (ACF) and partial autocorrelation function (PACF). Seasonal plots were generated for weekly and yearly pattern by using daily and monthly data, respectively.  To generate the seasonal plots, the data was first deconstructed based on its period. For daily data, the weekly period was used; while for monthly data, the yearly period was used. The weekly period was obtained by creating an ordered value formatted as year - week, e.g. `2018 - W01`. Similarly, monthly period was obtained by creating an ordered value formatted as year - month, e.g. `2018 - M01`. We then grouped the series by its deconstructed period and visually examine seasonality as overlapping pattern in most periods. To substantiate the findings, ACF and PACF plots were used to check on statistical significance of a given pattern.
